---
title: "prompt analysis"
output:
  pdf_document: default
  html_document: default
date: '2024-10-09'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lme4)
library(multcomp)
```

# Data reformatting

```{r}
data.raw = read.csv('llama3p1_70b_base.csv',header=TRUE)
orig <- unique(subset(data.raw,select=c(1,2,8:10))) %>% rename(success = n_successes_original,
                                                       pass = pass1_original) %>% mutate(category = "Baseline",
                                                                                         intervention = "None",
                                                                                         original_word = NA)
subs <- subset(data.raw,select=-c(8:9)) %>% rename(success = n_successes_intervened,
                                                       pass = pass1_intervened,
                                                   category = intervention_category)

data <- rbind(orig,subs) %>% mutate(n = 200)
data$category <- fct_relevel(data$category,"Baseline")
data$intervention <- fct_relevel(data$intervention,"None")
```

# String interventions

```{r}
string.ps <- subset(data,category=="string")$prompt_id
strings <- subset(data,(category=="string"|category=="Baseline")&prompt_id %in% string.ps)
```

```{r}
string.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=strings,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(string.model)
```

# Dict interventions

```{r}
dict.ps <- subset(data,category=="dictionary")$prompt_id
dicts <- subset(data,(category=="dictionary"|category=="Baseline")&prompt_id %in% dict.ps)
```

```{r}
dict.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=dicts,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(dict.model)
```

# Integer interventions

```{r}
int.ps <- subset(data,category=="integer")$prompt_id
ints <- subset(data,(category=="integer"|category=="Baseline")&prompt_id %in% int.ps)
```

```{r}
int.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=ints,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(int.model)
```

# List interventions

```{r}
list.ps <- subset(data,category=="list")$prompt_id
lists <- subset(data,(category=="list"|category=="Baseline")&prompt_id %in% list.ps)
```

```{r}
list.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=lists,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(list.model)
```

# Key interventions

```{r}
key.ps <- subset(data,category=="key")$prompt_id
keys <- subset(data,(category=="key"|category=="Baseline")&prompt_id %in% key.ps)
```

```{r}
key.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=keys,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(key.model)
```

# Typecast interventions

```{r}
cast.ps <- subset(data,category=="typecast")$prompt_id
casts <- subset(data,(category=="typecast"|category=="Baseline")&prompt_id %in% cast.ps)
```

```{r}
cast.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=casts,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(cast.model)
```

# Concatenation interventions

```{r}
concat.ps <- subset(data,category=="concatenate")$prompt_id
concats <- subset(data,(category=="concatenate"|category=="Baseline")&prompt_id %in% concat.ps)
```

```{r}
concat.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=concats,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(concat.model)
```

# Insert/Append interventions

```{r}
append.ps <- subset(data,category=="insert")$prompt_id
appends <- subset(data,(category=="insert"|category=="Baseline")&prompt_id %in% append.ps)
```

```{r}
append.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=appends,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(append.model)
```

# Skip interventions

```{r}
skip.ps <- subset(data,category=="skip")$prompt_id
skips <- subset(data,(category=="skip"|category=="Baseline")&prompt_id %in% skip.ps)
```

```{r}
skip.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=skips,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(skip.model)
```

# Return interventions

```{r}
return.ps <- subset(data,category=="return")$prompt_id
returns <- subset(data,(category=="return"|category=="Baseline")&prompt_id %in% return.ps)
```

```{r}
return.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=returns,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(return.model)
```

# Loop through interventions

```{r}
loop.ps <- subset(data,category=="loop_through")$prompt_id
loops <- subset(data,(category=="loop_through"|category=="Baseline")&prompt_id %in% loop.ps)
```

```{r}
loop.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=loops,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(loop.model)
```

# Input interventions

## Take interventions

```{r}
take.ps <- subset(data,category=="take")$prompt_id
takes <- subset(data,(category=="take"|category=="Baseline")&prompt_id %in% take.ps)
```

```{r}
take.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=takes,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(take.model)
```

## Parameter interventions

```{r}
param.ps <- subset(data,category=="parameter")$prompt_id
params <- subset(data,(category=="parameter"|category=="Baseline")&prompt_id %in% param.ps)
```

```{r}
param.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=params,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(param.model)
```

## Provide interventions

```{r}
provide.ps <- subset(data,category=="provide")$prompt_id
provides <- subset(data,(category=="provide"|category=="Baseline")&prompt_id %in% provide.ps)
```

```{r}
provide.model <- glmer(pass ~ intervention + (1+intervention|problem) + (1|prompt_id), weights=n, data=provides,family="binomial",control=glmerControl(optimizer="bobyqa",calc.derivs = FALSE))
```

```{r}
summary(provide.model)
```


# Export results to Latex

```{r}
round_sig <- Vectorize(function(x, sig = 3) {
  # Handle special case for zero
  if (x == 0) return(0)
  
  # Calculate the factor to round to significant figures
  scale <- ceiling(log10(abs(x)))
  rounded_value <- round(x, sig - scale - 1)
  
  return(format(rounded_value, nsmall = 0, scientific = FALSE))
})

round_p <- Vectorize(function(x, sig = 3) {
  # Handle special case for zero
  x <- as.numeric(x)
  if (x < 0.0001) return("\\textbf{\\textless 0.0001}")
  
  # Calculate the factor to round to significant figures
  scale <- ceiling(log10(abs(x)))
  rounded_value <- round(x, sig - scale - 1)
  
  return(format(rounded_value, nsmall = 0, scientific = FALSE))
})
```

```{r}
model_summary <- tidy(string.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```

```{r}
model_summary <- tidy(list.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```

```{r}
model_summary <- tidy(int.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```

```{r}
model_summary <- tidy(dict.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```

```{r}
model_summary <- tidy(key.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```

```{r}
model_summary <- tidy(return.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```

```{r}
model_summary <- tidy(take.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```

```{r}
model_summary <- tidy(param.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```

```{r}
model_summary <- tidy(provide.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```

```{r}
model_summary <- tidy(cast.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```

```{r}
model_summary <- tidy(skip.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```

```{r}
model_summary <- tidy(loop.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```

```{r}
model_summary <- tidy(concat.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```

```{r}
model_summary <- tidy(append.model, effects = "fixed") %>%
  mutate(across(c(estimate, std.error, statistic,p.value), round_sig),
         across(c(p.value),round_p),
         term=str_replace(term,"intervention",""))

model_sum <- model_summary %>% dplyr::select(term:p.value)

# Create the LaTeX table
kable(model_sum, format = "latex", booktabs = TRUE, escape = FALSE,col.names = c("Fixed effects","$\\widehat{\\beta}$","SE","$z$","$p$"))

```
